Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-15 main.tex
not much

\subsection{From Skew Bifibrations to Contraction and Weakening}

@@

>>>>

\begin{proof}
  For $\Deri$, we construct its propositional encoding $\PE\Deri$ by
  translating every line into its proposional encoding. The rules
  $\rectif\mfaD$ and $\rectif\mexD$ are replaced by:
  \begin{equation*}
    \vlderivation{
      \vlin{\rectif\acD}{}{\Scons{u_x\vlor\PE{(Ax)}\vlor\PE{(Ax)}}}{
        \vlin{\fequ}{}{\Scons{(u_y\vlor u_z)\vlor(\PE{(Ax)}\vlor\PE{(Ax)})}}{
          \vlhy{\Scons{(u_y\vlor\PE{(Ax)})\vlor (u_z\vlor\PE{(Ax)})}}}}}
  \end{equation*}
  and
  \begin{equation*}
    \vlderivation{
      \vlin{\rectif\acD}{}{\Scons{e_x\vlan\PE{(Ax)}\vlor\PE{(Ax)}}}{
        \vlin{\me}{}{\Scons{(e_y\vlor e_z)\vlan(\PE{(Ax)}\vlor\PE{(Ax)})}}{
          \vlhy{\Scons{(e_y\vlan\PE{(Ax)})\vlor (e_z\vlan\PE{(Ax)})}}}}}
  \end{equation*}
  respectively. This gives us a derivation $\vlderivation{
    \vlde{\set{\wlD,\wrD,\acD,\rectif\acD,\me,\fequ}}{\PE\Deri}{\PE
      B}{ \vlhy{\PE A}}}$ with $\mapof{\PE\Deri}$ being equal to
  $\mapof\Deri$, modulo relabeling of of the binders. It has been
  shown in~\cite{str:07:RTA} that $\mapof{\PE\Deri}$ is a skew
  fibration (see
  also~\cite{hughes:invar,str:ral:tableaux19,str:RR-9048}). Hence,
  $\mapof\Deri$ is a skew fibration. \todo{show the other properties,
    once they are fixed}
\end{proof}
\subsection{From Skew Bifibrations to Contraction and Weakening}

@@

\begin{proof}
  Let $\PE\gA=\graphof{\PE A}$ and $\PE\gB=\graphof{\PE B}$ which are equal to $\gA$ and $\gB$, respectively, modulo relabeling of the binders. Thus, we can define $\PE\phi\colon\PE\gA\to\PE\gB$, which is a skew fibration as well. 
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
